\vspace{-1in} Demystifying the Computer Science \\PhD Admission in US Universities\\{\large A Guide for International Students

### 2023-11-02 demystify.tex
updates

\title{\vspace{-1in} Demystifying the Computer Science \\PhD Admission in US Universities\\{\large A Guide for International Students}}
%\date{\today}
\author{\small \href{https://nguyenthanhvuh.github.io}{ThanhVu (Vu) Nguyen} (\href{mailto:tvn@gmu.edu}{tvn@gmu.edu})}

@@

    This document is available on \href{https://github.com/nguyenthanhvuh/phd-cs-us}{Github}. If you have questions or comments, feel free to create a \href{https://github.com/nguyenthanhvuh/phd-cs-us/issues}{GitHub issue} for discussion.
\end{abstract}

@@

Second, I believe that applying to a good US university \emph{should not} be any
harder than at schools in other countries. If you believe you have a chance in other countries, e.g., South Korea, Singapore, Germany, UK, Japan and Australia, then you will surely have a chance in the US as well.

@@

\paragraph{Rankings} Faculty have a ranking, e.g., assistant, associate, full, regardless if they are tenure line or teaching.  Assistant means new faculty, associate means they have been promoted, and full means they are senior. A tenure track faculty starts with being an assistant professor and then gets tenure and promoted to associate (typically after 6 years) and then full (time varies, some become full within 3-4 years, some 10+ years, some remain associate).

@@

\subsection{Difference between PhD in the US and other countries}
Here we summarize the main differences between CS PhD in the US and other countries.  This is based on my experience and what I heard from others who did PhD in other countries.

>>>>

\title{\vspace{-1in} Demystifying the Computer Science \\PhD Admission in US Universities\\{\large A Guide for International Students}}
%\date{\today}
\author{\href{https://nguyenthanhvuh.github.io}{ThanhVu (Vu) Nguyen} (\href{mailto:tvn@gmu.edu}{tvn@gmu.edu})\\{\small George Mason University, Dept. of Computer Science}}

@@

    The latest version of document is at \url{https://nguyenthanhvuh.github.io/phd-cs-us/demystify.pdf} and its \LaTeX{} source is on \href{https://github.com/nguyenthanhvuh/phd-cs-us}{Github}. If you have questions or comments, feel free to create a \href{https://github.com/nguyenthanhvuh/phd-cs-us/issues}{GitHub issue} for discussion.
\end{abstract}

@@

Second, I believe that applying to a good US university \emph{should not} be any
harder than at schools in other countries. If you believe you have a chance in other countries, e.g., South Korea, Singapore, Germany, UK, Japan and Australia, then you will surely have a chance in the US as well\footnote{\S\ref{sec:non-us-differences} compares CS PhD study in the US to other countries.}.

@@

\paragraph{Rankings} Faculty have ranking, e.g., assistant, associate, full, regardless if they are tenure line or teaching.  Assistant means new faculty, associate means they have been promoted, and full means they are senior. A tenure track faculty starts with being an assistant professor and then gets tenure and promoted to associate (typically after 6 years) and then full (time varies, some become full within 3-4 years, some 10+ years, some remain associate).

@@

\subsection{Difference between PhD in the US and other countries}\label{sec:non-us-differences}
Here we summarize the main differences between CS PhD in the US and other countries.  This is based on my experience and what I heard from others who did PhD in other countries.
